%# -*- coding: utf-8-unix -*-
% !TEX program = xelatex
% !TEX root = ../thesis.tex
% !TEX encoding = UTF-8 Unicode
%TC:ignore
\begin{thanks}
	
This is the most important stage of my life as I am graduating from the most prestigious
institute ‘Shanghai Jiao Tong University (SJTU)’. Two and half years of studies at SJTU not
only provided me with rich contents of research but also polished my professional skills. Armed
with these tools and skills, I am ready to take on new challenges in life and pursue my dreams.
First of all, I would like to thank my supervisor Professor Wang Lin for guiding me
throughout my research and study. From discussing my research interests to this moment, even
changing my research topic, she has been very helpful throughout this journey. I am very grateful
to her for allowing me to explore my own capabilities and demonstrate my research attitude.
I would also like to thank all my lab mates who accompanied me throughout this project:
I want to thank them for the joy, laughter and occasional little surprises they brought to me,
adding a lot of warmth to my dull postgraduate life. They inspired me in every communication
with them and helped me make important decisions in life. Knowing each other is a precious
memory in my life and I hope this friendship lasts forever.
Finally, I would like to thank my parents and family who have always loved me and took
care of me with their unconditional love, care, and support. I have no words that can express my
gratitude for what they have done for me. Thank you!

\end{thanks}
%TC:endignore
